Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-09-03 paper.tex
clear -> clearly

Another interesting question is which sampling pattern is more powerful?
Our results shown in \cref{fig:comparison_patterns} clear illustrate that
for isotropic structure all sampling techniques provide quite similar results.
The differences, of course, will be significant for isotropic cases and
directional 3-point CFs calculations. Again, the clear winner here is not obvious.
Right-triangular pattern allows to systematically sample the structure with
predefined direction. On the other hand, equilateral triangle allows to
minimize the volume of computed functions and represent them as single curve,
similar to 2-point functions. Random pattern could be useful for rigorous bounds.
So, the better approach can depend on the problem at hand. Nonetheless,
the direct comparison of patterns can be performed only on the basis of
information content -- something we discuss in the next paragraph.

>>>>

Another interesting question is which sampling pattern is more powerful?
Our results shown in \cref{fig:comparison_patterns} clearly illustrate that
for isotropic structure all sampling techniques provide quite similar results.
The differences, of course, will be significant for isotropic cases and
directional 3-point CFs calculations. Again, the clear winner here is not obvious.
Right-triangular pattern allows to systematically sample the structure with
predefined direction. On the other hand, equilateral triangle allows to
minimize the volume of computed functions and represent them as single curve,
similar to 2-point functions. Random pattern could be useful for rigorous bounds.
So, the better approach can depend on the problem at hand. Nonetheless,
the direct comparison of patterns can be performed only on the basis of
information content -- something we discuss in the next paragraph.
